Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-11 doc/reviews/ResponseToReviewer1.tex

\noindent
\comment{Line 50: typo: ``well-known"}
\begin{itemize}
  \item This typo is corrected.
\end{itemize}

\noindent
\comment{Page 3: the first two paragraphs seem to be a bit disconnected
from the rest of the introduction. Maybe the authors should rewrite that
part so that there is a transition from the physical problem into
consideration to the various numerical methods used in the literature to
simulate it.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 70: ``we maintain contact-free suspensions with a
relatively weak non-stiff repulsive force". What do you mean by
relatively weak repulsive force ? Weak compared to what? (see additional
question on this hereinafter).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item We deleted the redundant equation (2.5) mentioned by the Reviewer.
\end{itemize}

@@

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
\end{itemize}

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. 
A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
when using a relatively large time step.

@@

% what we solve for?
\ReviewerOne{To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
After calculating the imposed forces $\FF_i$ and torques $T_i$, 
two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.}

@@

\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
results generated by using the algorithm in \cite{qua-vee-you2019} (refer to all figure insets in 
Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows trajectory 
comparisons between the proposed model and the continuum modeling for both shear flow and
extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$ represents the distance
between two centroids of JP vesicles. The centroid positions are identical for both models and the
geometry in the continuum model is created along the midplane locations of JP vesicles and the initial
reduced area is matched. Panel (a) shows that the results of continuum model does not have a 
periodic motion and two vesicles flow apart after 1.5 $\mu$s. Panel (b) shows that the results of
continuum model has similar trend of dynamics with one in the proposed model.}

>>>>

%%%% moved to new section 3.4

%\subsection{Time Marching}
%By solving the mobility problem, we obtain translational and angular
%velocities of the $N_b$-body system. 
%A second-order Adams-Bashforth
%scheme updates the particle positions and orientations. By including the
%repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
%when using a relatively large time step.

@@

% what we solve for?
\ReviewerOne{
\subsection{Time Marching}
To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
After calculating the imposed forces $\FF_i$ and torques $T_i$, 
two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
%By solving the mobility problem, we obtain translational and angular
%velocities of the $N_b$-body system. 
Moreover, a second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
}

@@

\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
insets in Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows 
trajectory comparisons between the proposed model and the continuum modeling for both 
shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
represents the distance between two centroids of JP vesicles. The centroid positions are 
identical for both models and the geometry in the continuum model is created along the 
midplane locations of JP vesicles and the initial reduced area is matched. Panel (a) shows that 
the results of continuum model does not have a periodic motion and two vesicles flow apart 
after 1.5 $\mu$s. Panel (b) shows that the results of continuum model has similar trend of
dynamics with one in the proposed model.}
